---
title: "Assignment B-1"
output: github_document
---

### Making a function  

This document is a solution to questions stated in the assignment. It covers making a function in R, documenting it, and testing it.  

### Setup  

Loading the required packages

```{r}

library(datateachr)
library(tidyverse)
library(testthat) 

```


### Exercise 1 and 2: Make and Document your Function  

A plotting function has been made as part of this exercise.  

1. This function accepts a  dataframe, grouping column, slicing number as a parameter.  
2. It then groups the entities of the column and counts the number of entries in each group.  
3. The output is then plotted as a bar chart, as per the slicing number.

```{r}
#' Function to group and plot the count of a column
#' 
#' This function is used to group a column, count the number of entries per group and plot a bar graph with number of bars as specified by the user.  
#' 
#' @param data_frame The dataframe on which the function is to be applied.
#' @param group_column The column of the dataframe which is to be grouped.
#' @param num The number of top entries to be displayed in the bar chart.
#' @returns A bar chart showing count of each grouped entity.
#' @example group_barchart(diamond, cut)

# Function that groups a column and plots the counted rows in each group
group_barchart <- function(data_frame, group_variable, num, ...){
  label <- rlang::englue("Number of entries for each {{group_variable}}")
  
  if(!is.numeric(num)) {
    stop('I am so sorry, but this function only works for numeric input!\n',
         'You have provided an object of class: ', class(num)[1])
  }
  
  data_frame %>%
    group_by({{group_variable}}) %>%
    summarise(count = n()) %>%
    slice_max(count, n = num) %>%
    ggplot(mapping = aes(x = {{group_variable}}, y = count, fill = {{group_variable}})) +
    geom_bar(stat="identity") +
    geom_text(aes(label=count), vjust=-0.3, size=3.5) +
    labs(title = label)+
    theme(plot.title = element_text(hjust=0.5))
  }

```


### Exercise 3: Include examples  


Examples of the function implementation have been shown below.  

```{r}
# First 6 rows of the diamond dataframe have been first analysed to choose the column to be grouped.

head(diamonds)
```

```{r}
# In order to determine which cut is popular, group_barchart function has been used to make a bar chart.
group_barchart(diamonds, cut, 3)

```
```{r}
# First 6 rows of the vancouver_trees dataframe have been first analysed to choose the column to be grouped.

head(vancouver_trees)
```
```{r}
# In order to determine which street_side_name is popular, group_barchart function has been used to make a bar chart.   
group_barchart(vancouver_trees, species_name, 5)
```

### Exercise 4: Test the Function  


Three different test_that functions have been written in order to test the working of the function.  

```{r}
# Testing if ggplot object is returned
test_that("Plot returns ggplot object",{
  chart_1 <- group_barchart(diamonds, cut, 2)
  expect_is(chart_1,"ggplot")
})


# Testing if the axis label is the same as column to be grouped
test_that("Scale is labelled 'species_name'",{
  chart_2 <- group_barchart(vancouver_trees, species_name, 10)
  expect_identical(chart_2$labels$x, "species_name")
})

## Testing if the plot is being printed
test_that("Printing ggplot object actually works",{
    chart_3 <- group_barchart(diamonds, cut, 5)
    expect_error(print(chart_3), NA)})
```