---
title: "Mini Data Analysis Milestone 2"
output: github_document
---

### Assignment B-1: Making a function  

This document is a solution to questions states in the assignment. It covers making a function in R, documenting it, and testing it.  

### Setup  

Loading the required packages

```{r}

library(datateachr)
library(tidyverse)
library(testthat)

```


### Exercise 1 and 2: Make and Document your Function  

A plotting function has been made as part of this exercise.  

1. This function accepts a  dataframe and grouping column as a parameter.  
2. It then groups the entities of the column and counts the number of entries in each group.  
3. The output is then plotted as a bar chart.  
```{r}
#' Function to group and plot the count of a column
#' 
#' This function is used to group a column, count the number of entries per group and plot a bar graph.
#' 
#' @param data_frame The dataframe on which the function is to be applied.
#' @param group_column The column of the dataframe which is to be grouped.
#' @returns A bar chart showing count of each grouped entity.
#' @example group_barchart(diamond, cut)

# Function that groups a column and plots the counted rows in each group
group_barchart <- function(data_frame, group_variable,...){
  label <- rlang::englue("Number of entries for each {{group_variable}}")
  
  data_frame %>%
  group_by({{group_variable}}) %>%
  summarise(count = n()) %>%
  arrange(desc({{group_variable}})) %>%
  ggplot(mapping = aes(x = {{group_variable}}, y = count)) +
  geom_bar(stat="identity") +
  labs(title = label)
}

```


### Exercise 3: Include examples  


Examples of the function implementation have been shown below.  

```{r}
# First 6 rows of the diamond dataframe have been first analysed to choose the column to be grouped.

head(diamonds)
```

```{r}
# In order to determine which cut is popular, group_barchart function has been used to make a bar chart.
group_barchart(diamonds, cut)
```
```{r}
# First 6 rows of the vancouver_trees dataframe have been first analysed to choose the column to be grouped.

head(vancouver_trees)
```
```{r}
# In order to determine which street_side_name is popular, group_barchart function has been used to make a bar chart.   
group_barchart(vancouver_trees, street_side_name)
```

### Exercise 4: Test the Function  


Three different test_that functions have been written in order to test the working of the function.  

```{r}
# Testing if ggplot object is returned
test_that("Plot returns ggplot object",{
  p <- group_barchart(diamonds, cut)
  expect_is(p,"ggplot")
})


# Testing if the axis label is the same as column to be grouped
test_that("Scale is labelled 'cut'",{
  p <- group_barchart(diamonds, cut)
  expect_identical(p$labels$x, "cut")
})

## Testing if the plot is being printed
test_that("Printing ggplot object actually works",{
    p <- group_barchart(diamonds, cut)
    expect_error(print(p), NA)})
```